Manuscript draft

### 2019-06-03 manuscript/manuscript draft.Rmd
updated manuscript draft

It is understood that the productivity of forests shows variation with latitude, with a general trend of increasing productivity towards the tropics; however the exact nature of this pattern and the mechanisms that drive it are poorly understood. Climate can be an important driver of productivity, particularly on a global scale; achieving a better understanding of the climatic controls on forest productivity will help to illuminate potential responses and feedbacks of forests to climate change.

>>>>

The productivity of forests shows variation with latitude, with a general trend of increasing productivity towards the tropics; however the exact nature of this pattern and the mechanisms that drive it are poorly understood. Climate can be an important driver of productivity, particularly on a global scale; achieving a better understanding of the climatic controls on forest productivity will help to illuminate potential responses and feedbacks of forests to climate change.
